Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2024-09-08 Observations_SAM_SS3_Krill_481.Rmd
commit add html 9 sept

---
title: "Recommentations: Integrated approach to modeling krill population dynamics in Western Antarctic Peninsula. Spatial and ecosystem considerations"
subtitle: "Appendix 1 WP- SAM 2024/26"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    number_sections: false
fig_caption: yes
bibliography: SA_krill.bib
csl: apa.csl
link-citations: yes
toc: false
linkcolor: blue
linestretch: 1.3
header-includes:
- \fontsize{12}{16}
- \selectfont
- \usepackage{lscape}
---
\newpage
\tableofcontents
\newpage

>>>>

---
title: "APPENDIX 1: Integrated approach to modeling krill population dynamics in Western Antarctic Peninsula. Spatial and ecosystem considerations"
subtitle: "Observations WP- SAM 2024/26"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    number_sections: false
fig_caption: yes
bibliography: SA_krill.bib
csl: apa.csl
link-citations: yes
toc: false
linkcolor: blue
linestretch: 1.3
header-includes:
- \fontsize{12}{16}
- \selectfont
- \usepackage{lscape}
---
\newpage
\tableofcontents
\newpage

### 2024-09-08 SS3_Krill_481_FSA.Rmd
commit add html 9 sept

date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    number_sections: false
fig_caption: yes
bibliography: SA_krill.bib
csl: apa.csl
link-citations: yes
toc: false
linkcolor: blue
linestretch: 1.3
header-includes:
- \fontsize{12}{16}
- \selectfont
- \usepackage{lscape}
---
\newpage
\tableofcontents
\newpage

@@

Retrospective analysis shows the pattern of bias that exists in the models and is one of the ways in which we have identified that in all the tested scenarios there is a pattern, however, model S1 is the one that performs better. @Carvalho2021b indicate that values of rho parameter that fall outside (-0.15 to 0.20) for SSB for longer-lived species, or outside (-0.22 to 0.30) for shorter-lived species indicates an undesirable retrospective pattern (Figure \@(fig:retros1)). To evaluate the overall model fit of the relative abundance indices and composition data in `s1`, we used the joint-index residual. Overall, `s1` had a good performance when evaluating the lengths compositions (14.2%), however  RMSE showed a low predictive power with respect to the indices (71.3%). A loess-smoother indicated there appeared to be increased variability in the residuals of model fit to CPUE over time (Figure \@ref(fig:rmses1)).

@@

```{r recdev, out.width='90%', fig.cap="Recruit deviation for all scenarios in krill population"}
knitr::include_graphics('index_files/figure-html/unnamed-chunk-47-1.jpeg')
```

>>>>

date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    number_sections: false
fig_caption: yes
bibliography: SA_krill.bib
always_allow_html: true
csl: apa.csl
link-citations: yes
toc: false
linkcolor: blue
linestretch: 1.3
header-includes:
- \fontsize{12}{16}
- \selectfont
- \usepackage{lscape}
---
\newpage
\tableofcontents
\newpage

@@

Retrospective analysis shows the pattern of bias that exists in the models and is one of the ways in which we have identified that in all the tested scenarios there is a pattern, however, model S1 is the one that performs better. @Carvalho2021b indicate that values of rho parameter that fall outside (-0.15 to 0.20) for SSB for longer-lived species, or outside (-0.22 to 0.30) for shorter-lived species indicates an undesirable retrospective pattern (Figure \@ref(fig:retros1)). To evaluate the overall model fit of the relative abundance indices and composition data in `s1`, we used the joint-index residual. Overall, `s1` had a good performance when evaluating the lengths compositions (14.2%), however  RMSE showed a low predictive power with respect to the indices (71.3%). A loess-smoother indicated there appeared to be increased variability in the residuals of model fit to CPUE over time (Figure \@ref(fig:rmses1)).

@@

```{r recdev, out.width='90%', fig.cap="Recruit deviation for all scenarios in krill population"}
knitr::include_graphics('Figs/recruitdev.png')
```

### 2024-09-08 index.Rmd
commit add html 9 sept

```{r fig.width=8, fig.height=7}
dev01 <- base.model01$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S01")
dev1 <- base.model1$recruit[1:43,c(1,7)]%>% 
  mutate(Serie = "S1")
dev2 <- base.model2$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S2")
dev3 <- base.model3$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S3")
dev4 <- base.model4$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S4")
dev5 <- base.model5$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S5")
dev6 <- base.model6$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S6")
dev7 <- base.model7$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S7")

>>>>

```{r}
dev01 <- base.model01$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S01")
dev1 <- base.model1$recruit[1:43,c(1,7)]%>% 
  mutate(Serie = "S1")
dev2 <- base.model2$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S2")
dev3 <- base.model3$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S3")
dev4 <- base.model4$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S4")
dev5 <- base.model5$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S5")
dev6 <- base.model6$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S6")
dev7 <- base.model7$recruit[1:43,c(1,7)] %>% 
  mutate(Serie = "S7")
